---
title: "Machine Learning I: Group Assignment 2: Supervised"
author: "Group E"
date: "2/JUL/2020"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float:
      collapsed: true
---
<style>
.html-widget {
    margin: auto;
}
</style>

```{r setup, include=FALSE, eval=TRUE}
knitr::opts_chunk$set(message = FALSE, echo=TRUE, warning=FALSE)
```

```{r, echo=FALSE}
library(tidyverse)
library(readxl)
library(skimr)
library(MASS)
library(leaflet)
library(PerformanceAnalytics)
library(gmodels)
library(htmltools)
library(flipPlots)
library(viridisLite)
```

# Reading data

```{r}
data <- read_excel(path = file.path('data', 'Houses for rent in madrid_assignment 2020.xlsx'), sheet = 'Houses_for_rent_madrid_assignme')
# skim(data)
```

# Data preparation

Some data preparation was done to the RAW data.\
Including:\
* Normalization at the address\
* Extraction of property type from the description\
* Completion of data\
  * For the **Chalet**: Floor, Outer and Elevator were revised\
  * For **Estudio**: Bedrooms were revised\
  * For **Chalet pareado**: Floor and Outer were revised\
  * For **Chalet adosado**: Floor and Outer were revised\
\
A summary of the data is presented.

```{r}
data1 <- data %>% 
  mutate(
    Type = factor(ifelse(grepl('^Piso\\sen', Address), 'Piso',
                  ifelse(grepl('^Ático\\sen', Address), 'Ático',
                  ifelse(grepl('^Dúplex\\sen', Address), 'Dúplex',
                  ifelse(grepl('^Estudio\\sen', Address), 'Estudio',
                  ifelse(grepl('^Chalet\\spareado\\sen', Address), 'Chalet pareado',
                  ifelse(grepl('^Chalet\\sadosado\\sen', Address), 'Chalet adosado',
                  ifelse(grepl('^Caserón\\sen', Address), 'Chalet',
                  ifelse(grepl('^Casa\\so\\schalet\\sindependiente\\sen', Address), 'Chalet',
                  ifelse(grepl('^Chalet\\sen', Address), 'Chalet', 'Other')))))))))),
    # Fix Area
    Area = gsub('\\s-\\s', '-', Area),
    Area = gsub('^en\\s', '', Area),
    Area = gsub('chalet independiente en Nueva España', 'Nueva España', Area),
    # Chalet
    Floor = ifelse(is.na(Floor) & Type == 'Chalet', 0, Floor),
    Outer = ifelse(is.na(Outer) & Type == 'Chalet', 0, Outer),
    Elevator = ifelse(is.na(Elevator) & Type == 'Chalet', 0, Elevator),
    # Estudio
    Bedrooms = ifelse(is.na(Bedrooms) & Type == 'Estudio', 0, Bedrooms),
    # Chalet pareado
    Floor = ifelse(is.na(Floor) & Type == 'Chalet pareado', 0, Floor),
    Outer = ifelse(is.na(Outer) & Type == 'Chalet pareado', 0, Outer),
    # Chalet adosado
    Floor = ifelse(Type == 'Chalet adosado', 0, Floor), # Data error
    Outer = ifelse(is.na(Outer) & Type == 'Chalet adosado', 0, Outer),
    # Factoring
    Outer = factor(Outer, levels = c(0, 1), labels = c('No', 'Yes')),
    Elevator = factor(Elevator, levels = c(0, 1), labels = c('No', 'Yes')),
    # Type, but will be removed
    Penthouse = factor(Penthouse, levels = c(0, 1), labels = c('No', 'Yes')), # Ático
    Cottage = factor(Cottage, levels = c(0, 1), labels = c('No', 'Yes')), # Casa o chalet independiente, Caserón, Chalet, Chalet adosado, Chalet pareado
    Duplex = factor(Duplex, levels = c(0, 1), labels = c('No', 'Yes')), # Dúplex
    Semidetached = factor(Semidetached, levels = c(0, 1), labels = c('No', 'Yes')) #Chalet, Chalet adosado
  )
skim(data1)
```

# Feature engineering
## Adding geolocalization

Using the project http://nominatim.openstreetmap.org, we had converted the properties addresses to latitude and longitude.\
This allows a better representation of the properties in a map, and also better for the **regression model**.\
\
Only 50 addresese were not possible to map.

```{r}
# https://datascienceplus.com/osm-nominatim-with-r-getting-locations-geo-coordinates-by-its-address/
## geocoding function using OSM Nominatim API
## details: http://wiki.openstreetmap.org/wiki/Nominatim
## made by: D.Kisler 

# Function to geolocate
nominatim_osm <- function(address = NULL)
{
  if(suppressWarnings(is.null(address)))
    return(data.frame())
  tryCatch(
    d <- jsonlite::fromJSON( 
      gsub('\\@addr\\@', gsub('\\s+', '\\%20', address), 
           'http://nominatim.openstreetmap.org/search/@addr@?format=json&addressdetails=0&limit=1')
    ), error = function(c) return(data.frame())
  )
  if(length(d) == 0) return(data.frame())
  return(data.frame(address = address, lon = as.numeric(d$lon), lat = as.numeric(d$lat)))
}

# Full address
data2_temp <- data1 %>% 
  mutate(AddressComplete = gsub(".*\\sen\\s","", Address),
         AddressComplete = paste(AddressComplete, ifelse(is.na(Number), 1, Number), Area, 'Madrid', 'Spain', sep = ', '),
         AreaComplete = paste(Area, 'Madrid', 'Spain', sep = ', '))

# Group full address
data_3_temp <- data2_temp %>% 
  group_by(AddressComplete) %>% 
  summarize(n=n())

# Look for the geolocalization
# system.time({
#   data_geopos_address <- lapply(data_3_temp$AddressComplete, nominatim_osm) %>%
#     bind_rows()
# })
# saveRDS(object = data_geopos_address, file = file.path('storage', 'data_geopos_address.RData'))
data_geopos_address <- readRDS(file = file.path('storage', 'data_geopos_address.RData'))

# Group area
data_3_temp <- data2_temp %>% 
  filter(!AddressComplete %in% data_geopos_address$address) %>% 
  group_by(AreaComplete) %>% 
  summarize(n=n())

# Look for the geolocalization
# system.time({
#   data_geopos_area <- lapply(data_3_temp$AreaComplete, nominatim_osm) %>%
#     bind_rows()
# })
# saveRDS(object = data_geopos_area, file = file.path('storage', 'data_geopos_area.RData'))
data_geopos_area <- readRDS(file = file.path('storage', 'data_geopos_area.RData'))

data_3_temp <- data2_temp %>% 
  left_join(data_geopos_address, by = c("AddressComplete" = "address")) %>% 
  left_join(data_geopos_area, by = c("AreaComplete" = "address")) %>% 
  mutate(Longitude = ifelse(is.na(lon.x), lon.y, lon.x),
         Latitude = ifelse(is.na(lat.x), lat.y, lat.x)) %>% 
  dplyr::select(-lon.x, -lat.x, -lon.y, -lat.y)
```

## Data selection

Because of the new latitude and longitud data, we are able to remove from the input dataset the **Addrees**, **Number**, **Area** and **District**.\
\
The following summary is a representation of the input for the **regression model**.

```{r}
data4 <- data_3_temp %>% 
  dplyr::select(-Penthouse, -Cottage, -Duplex, -Semidetached) %>% # 'Type' is more comprehensive
  filter_at(vars(Outer, Elevator, Bedrooms, Floor, Latitude, Longitude), all_vars(!is.na(.))) # Remove nulls

data5 <- data4 %>% 
  dplyr::select(-Address, -Number, -Area, -District) %>% # Replaced by lat and lon.
  dplyr::select(-Id, -AddressComplete, -AreaComplete)

skim(data5)
```

# Correlation
There is a high correlation between the **Rent** price and **Sq.Mt** (flat dimension of the property), and also with the number of **Bedrooms**.\
The number of **Floor** of the property, has less significance to the dependent variable **Rent**.

```{r}
# C:\Users\juanb\OneDrive\GMBD\2020-01-10 - TERM 1\STATISTICAL PROGRAMMING - R (MBD-EN-BL2020J-1_32R369_316435)\Group assignment\GitHub\gmbd_r\!Delivery\EDA-1.R

data5 %>% 
  # dplyr::select(Bedrooms, Sq.Mt, Floor, Longitude, Latitude) %>% 
  dplyr::select_if(is.numeric) %>% 
  chart.Correlation(histogram=TRUE)
```

# Frequency tables

```{r, R.options = list(width = 200)}
# https://dabblingwithdata.wordpress.com/2017/12/20/my-favourite-r-package-for-frequency-tables/

CrossTable(data4$Elevator, data4$Type, expected = FALSE, prop.t = FALSE, prop.chisq = FALSE)
CrossTable(data4$Outer, data4$Type, expected = FALSE, prop.t = FALSE, prop.chisq = FALSE)
CrossTable(data4$Bedrooms, data4$Type, expected = FALSE, prop.t = FALSE, prop.chisq = FALSE)
CrossTable(data4$Floor, data4$Type, expected = FALSE, prop.t = FALSE, prop.chisq = FALSE)
```

# Sankey

```{r}
# https://www.displayr.com/how-to-create-sankey-diagrams-from-tables-using-r/
# install.packages("devtools")
# library(devtools)
# install_github("Displayr/flipPlots")
data1 %>% 
  dplyr::select(Type, Outer, Elevator, Bedrooms, Floor) %>% 
  SankeyDiagram(link.color = "Source") 

data1 %>% 
  dplyr::select(District, Type) %>% 
  SankeyDiagram(link.color = "Target", max.categories = 300) 
```

# Densities

```{r}
# data4 %>% 
#   ggplot(aes(x = Sq.Mt, color = Type)) +
#   # geom_histogram(aes(y=..density..)) +
#   geom_density(alpha=.2) +
#   labs(x = 'Log10(Sq.Mt)', y = 'Density')
# 
# data4 %>%
#   ggplot(aes(x = Bedrooms, color = Type)) +
#   # geom_histogram(aes(y=..density..)) +
#   geom_density(alpha=.2) +
#   labs(x = 'Bedrooms', y = 'Density')

library(ggridges)
# http://www.sthda.com/english/articles/32-r-graphics-essentials/133-plot-one-variable-frequency-graph-density-distribution-and-more/
theme_set(theme_ridges())

data4 %>% 
  ggplot(aes(x = Sq.Mt, y = Type)) +
  # geom_histogram(aes(y=..density..)) +
  geom_density_ridges(aes(fill = Type), alpha=.2) +
  labs(x = 'Sq.Mt', y = 'Density') +
  theme(legend.position = "none")

data4 %>%
  ggplot(aes(x = Bedrooms, y = Type)) +
  # geom_histogram(aes(y=..density..)) +
  geom_density_ridges(aes(fill = Type), alpha=.2) +
  labs(x = 'Bedrooms', y = 'Density') +
  theme(legend.position = "none")

data4 %>%
  ggplot(aes(x = Floor, y = Type)) +
  # geom_histogram(aes(y=..density..)) +
  geom_density_ridges(aes(fill = Type), alpha=.2) +
  labs(x = 'Floor', y = 'Density') +
  theme(legend.position = "none")

data4 %>%
  ggplot(aes(x = Sq.Mt)) +
  stat_ecdf(aes(color = Type, linetype = Type), geom = "step", size = 1) +
  labs(y = "f(Sq.Mt)")

data4 %>%
  ggplot(aes(x = Bedrooms)) +
  stat_ecdf(aes(color = Type, linetype = Type), geom = "step", size = 1) +
  labs(y = "f(Bedrooms)")
```

# Impact of removing one feature at a time

```{r}
bind_cols(
  FeatureRemoved = c('None', colnames(data5)[2:length(colnames(data5))]),
bind_rows(
  coef(glm(Rent ~ ., data = data5, family = gaussian(link = "identity"))),
  coef(glm(Rent ~ . - Bedrooms, data = data5, family = gaussian(link = "identity"))),
  coef(glm(Rent ~ . - Sq.Mt, data = data5, family = gaussian(link = "identity"))),
  coef(glm(Rent ~ . - Floor, data = data5, family = gaussian(link = "identity"))),
  coef(glm(Rent ~ . - Outer, data = data5, family = gaussian(link = "identity"))),
  coef(glm(Rent ~ . - Elevator, data = data5, family = gaussian(link = "identity"))),
  coef(glm(Rent ~ . - Type, data = data5, family = gaussian(link = "identity"))),
  coef(glm(Rent ~ . - Longitude, data = data5, family = gaussian(link = "identity"))),
  coef(glm(Rent ~ . - Latitude, data = data5, family = gaussian(link = "identity"))))
)
```

# Summary per factor

```{r}
summary_factor <- function(factor_){
  data4 %>% 
    group_by_at(all_of(factor_)) %>% 
    summarise(Mean=mean(Rent), SD=sd(Rent), N=n(),
              p0.25 = quantile(Rent, probs = 0.25), 
              p0.50 = quantile(Rent, probs = 0.50), 
              p0.75 = quantile(Rent, probs = 0.75),
              .groups = 'drop')
}

summary_factor('Outer')
summary_factor('Elevator')
summary_factor('Type')
summary_factor('Bedrooms')
summary_factor('Floor')

data4 %>% 
  mutate(Sq.MtRanges = cut(data4$Sq.Mt, breaks = 6)) %>% 
  group_by(Sq.MtRanges) %>% 
  summarise(Mean=mean(Rent), SD=sd(Rent), N=n(), 
            p0.25 = quantile(Rent, probs = 0.25), 
            p0.50 = quantile(Rent, probs = 0.50), 
            p0.75 = quantile(Rent, probs = 0.75),
            .groups = 'drop')

data4 %>% 
  mutate(Sq.MtRanges = cut(data4$Sq.Mt, breaks = 6)) %>% 
  ggplot(aes(x = Rent/Sq.Mt, y = Sq.MtRanges)) +
  # geom_histogram(aes(y=..density..)) +
  geom_density_ridges(aes(fill = Sq.MtRanges), alpha=.2) +
  labs(x = 'Rent/Sq.Mt', y = 'Sq.Mt range') +
  theme(legend.position = "none")

data4 %>% 
  mutate(Sq.MtRanges = cut(data4$Sq.Mt, breaks = 6)) %>% 
  ggplot(aes(x = Rent, y = Sq.MtRanges)) +
  # geom_histogram(aes(y=..density..)) +
  geom_density_ridges(aes(fill = Sq.MtRanges), alpha=.2) +
  labs(x = 'Rent', y = 'Sq.Mt range') +
  theme(legend.position = "none")
```

# Regression model

```{r}
# Fit full model
# model_full <- glm(Rent ~ ., data = data1)
# https://stats.stackexchange.com/questions/181113/is-there-any-difference-between-lm-and-glm-for-the-gaussian-family-of-glm
# full.model1 <- lm(Rent ~ ., data = data1)
model_full <- glm(Rent ~ ., data = data5, family = gaussian(link = "identity"))
summary(model_full)

# Step model
model_step <- model_full %>% 
  stepAIC(trace = TRUE)
summary(model_step)
```

# Good opportunities

```{r}
# Find good opportunities in the market looking for flats that may be under their theoretical estimated price

data_6_temp <- data4
data_6_temp$Prediction <- predict(model_step, data_6_temp)
data_6_temp$Ratio <- data_6_temp$Prediction/data_6_temp$Rent-1

data_6_temp %>% 
  arrange(desc(Ratio))
```

# Model summary table: Scaled

```{r}
# Scaled
data_7_temp <- data5 %>% 
  mutate_if(is.numeric, scale)
model_step_scaled <- glm(formula(model_step), data = data_7_temp, family = gaussian(link = "identity"))
summary(model_step_scaled)

# First version of the summary
summary_unit <- summary(model_step)$coefficients %>% 
  data.frame() %>% 
  rownames_to_column()
summary_scaled <- summary(model_step_scaled)$coefficients %>% 
  data.frame() %>% 
  rownames_to_column() %>% 
  rename_all(function(x) paste(x, 'scaled', sep = '_'))
bind_cols(summary_unit,
          dplyr::select(summary_scaled, Estimate_scaled, Std..Error_scaled, t.value_scaled))

# Second version of the summary
regression_table <- function(x, x_scaled, level = 0.95) {
  table <- cbind(
    summary(x)$coefficients,
    summary(x_scaled)$coefficients[, 'Estimate'],
    confint.default(x, level = level))
  colnames(table)[5] <- "Estimate Std."
  return(table)
}

regression_table(model_step, model_step_scaled)
```

# Map

```{r}
# Labels for the map ----
data_6_temp$Label <- 
  paste('<strong>', data_6_temp$Type, '</strong>', '<br/>', 
        'Location:', data_6_temp$AddressComplete, '<br/>',
        'Rent price:', round(data_6_temp$Rent, 1), 'EUR/month', '<br/>',
        'Theoretical rent price:', round(data_6_temp$Prediction, 1), 'EUR/month', '<br/>',
        'Id:', data_6_temp$Id
        ) %>% 
  lapply(HTML)
```

## Piso
Interesting opportunities for **Piso**.

```{r}
data_7_temp <- data_6_temp %>% 
  filter(Ratio>1, Type == 'Piso')

# make palette
# https://cran.r-project.org/web/packages/viridis/vignettes/intro-to-viridis.html
pallete_ <- colorNumeric(palette = magma(20), domain = range(data_7_temp$Ratio))

data_7_temp %>% 
  leaflet() %>%
    addProviderTiles(providers$CartoDB.Positron) %>% 
    addCircleMarkers(~Longitude, ~Latitude, 
                     popup = ~Label, 
                     label = ~Type,
                     color = ~pallete_(Ratio))
                     # clusterOptions = markerClusterOptions())
```

## Ático
Interesting opportunities for **Ático**.

```{r}
data_7_temp <- data_6_temp %>% 
  filter(Ratio>1, Type == 'Ático')

# make palette
# https://cran.r-project.org/web/packages/viridis/vignettes/intro-to-viridis.html
pallete_ <- colorNumeric(palette = magma(20), domain = range(data_7_temp$Ratio))

data_7_temp %>% 
  leaflet() %>%
    addProviderTiles(providers$CartoDB.Positron) %>% 
    addCircleMarkers(~Longitude, ~Latitude, 
                     popup = ~Label, 
                     label = ~Type,
                     color = ~pallete_(Ratio))
                     # clusterOptions = markerClusterOptions())
```

## Estudio
Interesting opportunities for **Estudio**.

```{r}
data_7_temp <- data_6_temp %>% 
  filter(Ratio>1, Type == 'Estudio')

# make palette
# https://cran.r-project.org/web/packages/viridis/vignettes/intro-to-viridis.html
pallete_ <- colorNumeric(palette = magma(20), domain = range(data_7_temp$Ratio))

data_7_temp %>% 
  leaflet() %>%
    addProviderTiles(providers$CartoDB.Positron) %>% 
    addCircleMarkers(~Longitude, ~Latitude, 
                     popup = ~Label, 
                     label = ~Type,
                     color = ~pallete_(Ratio))
                     # clusterOptions = markerClusterOptions())
```